---
output:
  html_document: default
---

```{r chunkopts, eval = TRUE, echo = FALSE}

knitr::opts_chunk$set(eval = TRUE, echo = FALSE, 
                      message = TRUE, 
                      warning = TRUE, 
                      tidy = FALSE, cache = FALSE, include = TRUE, dpi = 72, fig.width = 12, fig.height = 8, fig.align = "center", results = "markup")
options(knitr.kable.NA = "")

tf_abs <- function(f) system.file(file.path("extdata", f), package = "volleyreport")
kable_format <- "html"

```

<style>.main {width: 1100px;}

#main .nav-pills > li > a:hover {
  background-color: #18348E;
}

#main .nav-pills > li.active > a,
#main .nav-pills > li.active > a:hover,
#main .nav-pills > li.active > a:focus {
  background-color: #18348E;
}

h1,h2,h3,h4,h5,h6,legend{ color:#18348E; }

#content{ max-width: 95% }

#content pre { background:#f3f6f6; color:#404040; }
#content pre.sourceCode{ background-color: #FFF; }

#nav-top span.glyphicon { color:#18348E; }
a { color:#18348E; /*#060F6A;*/
}

#main a {
    background-image: linear-gradient(180deg,#18349e,#18349e);
    color:#18348e;
}

#postamble .date {
    color: #211103; /*#f8e5ee;*/
}

#content .highlighted{
    background:#FACB01;
}

#content .row > div {
  border: 1px solid grey;
}

#main .row > div {
  border: 1px solid grey;
}

</style>

```{r child=tf_abs("section_matchreport_header.Rmd")}
```

```{r child=tf_abs("section_matchreport_hometeam.Rmd")}
```

```{r child=tf_abs("section_matchreport_visitingteam.Rmd")}
```

```{r child=tf_abs("section_matchreport_footer.Rmd")}
```

`r if (vsx$shiny_progress) try(shiny::setProgress(value = 0.95, message = paste0("Converting to ", toupper(vsx$format))), silent = TRUE)`

