---
pagetitle: "`r paste0('Match report: ', datavolley::home_team(vsx$x), ' vs ', datavolley::visiting_team(vsx$x))`"
author: "<span></span>"
output:
  ovpaged::plain:
    toc: false
    number_sections: false
    auto_table_breaks: false
---

```{r chunkopts, eval = TRUE, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE, tidy = FALSE, cache = FALSE, include = TRUE, dpi = 175, fig.width = 12, fig.height = 8, fig.align = "center", results = "markup")
options(knitr.kable.NA = "")

tf_abs <- function(f) system.file(file.path("extdata", f), package = "volleyreport")
kable_format <- "html"

```

<style>
:root {
--pagedjs-margin-top: 0 !important;
--pagedjs-margin-bottom: 0 !important;
}
.wcol { padding-left: 2px; padding-right: 2px; }
.widetable { width: 100%; }
thead > tr { border: 1px solid `r vsx$css$header_colour` }
.mtbl { width: 100%; }
.mtbl > tbody > tr { background: #fff; }
.mtbl td, .mtbl th { vertical-align: top; padding: 3px; }
</style>


```{r}
if (vsx$shiny_progress) try(shiny::setProgress(value = 0.3, message = "Generating header"), silent = TRUE)
```

```{r mr1html, warning = FALSE, results = "asis"}

if (!is.null(vsx$header_extra_pre)) cat(vsx$header_extra_pre, "\n")

if (!is.null(vsx$icon)) {
    cat("<table class=\"mtbl\"><tr><td width=\"15%\">\n")
    cat("<p style=\"margin:0;\"><img src=\"", vsx$icon, "\" style=\"max-width: 90%; max-height: 90%;\" /></p>\n", sep = "")
    cat("</td>\n")
    cat("<td width=\"85%\">\n")
}

cat("<table class=\"mtbl\"><tr>\n")

cat("<td width=\"25%\">")
volleyreport:::vr_content_match_outcome(vsx, kable_format)
cat("</td>\n")

cat("<td width=\"17%\">")
volleyreport:::vr_content_match_date(vsx, kable_format)
cat("</td>\n")

cat("<td width=\"22%\">")
volleyreport:::vr_content_match_refs(vsx, kable_format)
cat("</td>\n")

cat("<td width=\"36%\">")
volleyreport:::vr_content_partial_scores(vsx, kable_format)
cat("</td></tr></table>\n")
if (!is.null(vsx$icon)) {
    cat("</td></tr></table>\n")
}
```

```{r mr_score_ev, warning = FALSE, eval = vsx$style %in% c("ov1"), results = "asis", fig.height = 18 / 25.4, fig.width = 210 / 25.4}
cat("\n<div style=\"margin-top:-2mm; margin-bottom:-2mm;\">\n")
p <- if (sum(vsx$x$point, na.rm = TRUE) < 2) NULL else volleyreport:::vr_content_score_evplot(vsx)
if (!is.null(p)) print(p)
cat("\n\n</div>\n")
```

```{r mr2_home_html, warning = FALSE, results = "asis"}
cat("<table class=\"mtbl\"><tr>\n")
cat("<td width=\"100%\">")
volleyreport:::vr_content_team_table(vsx, kable_format, which_team = "home")
cat("</td>\n")
cat("</tr></table>\n")

```

```{r mr3_home_html, warning = FALSE, results = "asis"}
cat("<table class=\"mtbl\"><tr>\n")
cat("<td width=\"18%\">")
volleyreport:::vr_content_team_staff(vsx, kable_format, which_team = "home")
cat("</td>\n")

cat("<td width=\"81%\">")
volleyreport:::vr_content_team_set_summary(vsx, kable_format, which_team = "home")
cat("</td>\n")
cat("</tr></table>\n")

```

```{r mr2_visiting_html, warning = FALSE, results = "asis"}
cat("<table class=\"mtbl\"><tr>\n")
cat("<td width=\"100%\">")
volleyreport:::vr_content_team_table(vsx, kable_format, which_team = "visiting")
cat("</td>\n")
cat("</tr></table>\n")

```

```{r mr3_visiting_html, warning = FALSE, results = "asis"}
cat("<table class=\"mtbl\"><tr>\n")
cat("<td width=\"18%\">")
volleyreport:::vr_content_team_staff(vsx, kable_format, which_team = "visiting")
cat("</td>\n")

cat("<td width=\"81%\">")
volleyreport:::vr_content_team_set_summary(vsx, kable_format, which_team = "visiting")
cat("</td>\n")
cat("</tr></table>\n")

```

```{r}
if (vsx$shiny_progress) try(shiny::setProgress(value = 0.8, message = "Generating footer"), silent = TRUE)
```

```{r fr0, warning = FALSE, results = "asis"}
cat("<div class=\"sectionblock\">\n<table class=\"mtbl\"><tr>\n")
## left-hand content panel
cat("<td width=\"83%\">\n")
```

```{r fr1, warning = FALSE, results = "asis"}
## team names
cat("<table class=\"mtbl\"><tr>\n")
cat0("<td width=\"50%\" style=\"font-size:", vsx$base_font_size * 10/12, "px; font-weight:bold; text-align:center; border-left:", vsx$css$border, "; border-top:", vsx$css$border, ";\">", vsx$meta$teams$team[1], "</td>\n")
cat0("<td width=\"50%\" style=\"font-size:", vsx$base_font_size * 10/12, "px; font-weight:bold; text-align:center; border-left:", vsx$css$border, "; border-top:", vsx$css$border, "; border-right:", vsx$css$border, ";\">", vsx$meta$teams$team[2], "</td>\n")
cat("</tr></table>\n")
cat("<table class=\"mtbl\"><tr>\n")
```

```{r fr2, warning = FALSE, results = "asis"}
## home team points by rot
if (vsx$style %in% c("ov1")) {
    cat("<td width=\"27%\">\n")
    if (!grepl("beach", vsx$file_type)) cat(volleyreport:::vr_content_points_by_rot(vsx, kable_format, which_team = "home"))
    cat("</td>\n")
} else {
    ## default, show points by rot vertically and other stuff next to it
    ## wtf? this doesn't work if it's an if { ...} else {...} block??
    if (!grepl("beach", vsx$file_type)) cat0("<td width=\"10%\" style=\"border-right:", vsx$css$border, ";\">\n")
    if (!grepl("beach", vsx$file_type)) cat(volleyreport:::vr_content_points_by_rot(vsx, kable_format, which_team = "home"))
    if (!grepl("beach", vsx$file_type)) cat("</td>\n")
    if (!grepl("beach", vsx$file_type)) cat("<td width=\"17%\">\n")
    if (grepl("beach", vsx$file_type)) cat("<td width=\"27%\">\n")
    hteach <- volleyreport:::vr_content_team_each(vsx, kable_format, which_team = "home")
    for (this in hteach) cat(this, "\n")
    cat("</td>\n")
}
```

```{r fr3, warning = FALSE, results = "asis"}
## middle content
cat0("<td width=\"46%\" style=\"border-right:", vsx$css$border, "; border-left:", vsx$css$border, ";\">\n")
volleyreport:::vr_content_kill_on_rec(vsx, kable_format, eval_codes = c("#", "+", "#+"), hdr = "1st Attack AFTER POSITIVE RECEPTION (+#)")
volleyreport:::vr_content_kill_on_rec(vsx, kable_format, eval_codes = c("-", "!", "-/"), hdr = "1st Attack AFTER NEGATIVE RECEPTION (-!)")
volleyreport:::vr_content_kill_in_trans(vsx, kable_format)
cat("</td>\n")
```

```{r fr4, warning = FALSE, results = "asis"}
## visiting team points by rot
if (vsx$style %in% c("ov1")) {
    cat("<td width=\"27%\">\n")
    if (!grepl("beach", vsx$file_type)) cat(volleyreport:::vr_content_points_by_rot(vsx, kable_format, which_team = "visiting"))
    cat("</td>\n")
} else {
    cat0("<td width=\"", if (!grepl("beach", vsx$file_type)) 17 else 27, "%\" style=\"border-right:", vsx$css$border, ";\">\n")
    vteach <- volleyreport:::vr_content_team_each(vsx, kable_format, which_team = "visiting")
    for (this in vteach) cat(this, "\n")
    cat("</td>\n")
    ## wtf? this doesn't work if it's an if { ...} block??
    if (!grepl("beach", vsx$file_type)) cat0("<td width=\"10%\">\n")
    if (!grepl("beach", vsx$file_type)) cat(volleyreport:::vr_content_points_by_rot(vsx, kable_format, which_team = "visiting"))
    if (!grepl("beach", vsx$file_type)) cat("</td>\n")
}
```

```{r fr5, warning = FALSE, results = "asis"}
cat("</tr></table>\n")
## the right-hand panel for the report legend
cat0("<td width=\"16.7%\">\n")
volleyreport:::vr_content_key(vsx, kable_format)
cat("</td>\n")

cat("</tr></table>\n</div>\n")
```

```{r footnotes, warning = FALSE, results = "asis"}
if (length(vsx$footnotes) > 0) cat0("<div style=\"float:right; font-size:", vsx$base_font_size * 8/12, "px;\">", paste(footnotes, collapse = " "), "</p>")
```

`r if (vsx$shiny_progress) try(shiny::setProgress(value = 0.95, message = paste0("Converting to ", toupper(vsx$format))), silent = TRUE)`

